Smoothing Algorithms for Variable Rate Models

### 2012-04-09 draft3_VRsmoothing.tex
Added abstract

\begin{abstract}
The abstract goes here. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah. Blah, blah, blah, blah, blah, blah, blah, blah, blah, blah.
\end{abstract}

\begin{IEEEkeywords}

\end{IEEEkeywords}

>>>>

\begin{abstract}
Standard state-space methods assume that the latent state evolves uniformly over time, and can be modelled with a discrete-time process synchronous with the observations. This may be a poor representation of some systems in which the state evolution displays discontinuities in its behaviour. For such cases, a variable rate model may be more appropriate; the system dynamics are conditioned on a set of random changepoints which constitute a marked point process. In this paper, new particle smoothing algorithms are presented for use with conditionally linear-Gaussian and conditionally deterministic dynamics. These are demonstrated on problems of financial modelling and target tracking. Results indicate that the smoothing approximations provide more accurate and more diverse representations of the state posterior distributions.
\end{abstract}

\begin{IEEEkeywords}
Bayesian inference, state-space model, variable rate, particle filter, filtering, smoothing
\end{IEEEkeywords}
